Storage challenges in heterogeneous environments

### 2017-12-02 paper.tex
addresses Jeff section 2 comments
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Current I/O interfaces are in large part treated as black boxes that offer
limited control in the form of \emph{magic numbers} or coarse-grain hints. With
few exceptions such as I/O sequentiality and alignment parameters, existing
interfaces allow applications to express intent or expose low-level system state
or configurability. In order to realize end-to-end application I/O optmizations,
both application runtime and storage system will need to be co-designed such that runtime
adapation of behavior based on data structure is possible.

@@

Both HPC and cloud-based systems are seeing rapid advancements towards
heterogeneity. For instance, Amazon Web Services offers a large array of node
and network capabilities including FPGA and GPU co-processors. Emerging storage
technologies such as NVMe and persistent memories are offered by cloud providers
and will be integrated in future HPC systems, but even existing storage systems
are struggling to exploit their full performance~\cite{xu:fast16-nova}. In fact, the increased
performance of next-generation media and networks suggests that future systems
may require a CPU per storage device~\cite{samuels:oss16}. And in order to support a
dynamic range of interfaces, internal sub-systems will need to be generic and
re-usable to support the diverse of demands of runtime systems.

@@

Increased interactions of the new interfaces and system architectures discussed
above further complicate the duties of the storage system. As developers start
to push application-specific optimizations into the storage system, the storage
system must continue to provide the semantics and guarantees that users have
come to expect. Code-hardened subsystems that use QoS, scheduling, and load
balancing must now account for this new dimension. This problem is especially
relevant for data-intensive HPC applications that need these internal
optimizations, such as scheduling and locality, to retrieve data from and store
data on heterogeneous hardware.

>>>>

Current I/O interfaces are in large part treated as black boxes that offer
limited control in the form of \emph{magic numbers} or coarse-grain hints. With
few exceptions such as I/O sequentiality and alignment parameters, existing
interfaces do not allow applications to express intent or expose low-level system state
or configurability. In order to realize {\it end-to-end} application I/O optmizations,
both application runtime and storage system will need to be co-designed such that runtime
adapation of behavior based on data structure is possible.

@@

Both HPC and cloud-based systems are seeing rapid advancements towards
heterogeneity. For instance, Amazon Web Services offers a large array of node
and network capabilities including FPGA and GPU co-processors. Moreover, AWS
offers an HPC service for users to compose their own HPC systems Emerging
storage technologies such as NVMe and persistent memories are offered by cloud
providers and will be integrated in future HPC systems, but even existing
storage systems are struggling to exploit their full
performance~\cite{xu:fast16-nova}. In fact, the increased performance of
next-generation media and networks suggests that future systems may require a
CPU per storage device~\cite{samuels:oss16}. And in order to support a dynamic
range of interfaces, internal sub-systems will need to be generic and re-usable
to support the diverse of demands of runtime systems.

@@

While not part of our explicit challenges outlined above, operational policies
become required as a consequence of the research directions we propose to
address our key challenges.  Increased interactions of the new interfaces and
system architectures further complicate the duties of the storage system. As
developers start to push application-specific optimizations into the storage
system, the storage system must continue to provide the semantics and
guarantees that users have come to expect. Code-hardened subsystems that use
QoS, admission control, management for failures/misbehaving devices, and load
balancing must now account for this new dimension.  This problem is especially
relevant for data-intensive HPC applications that need these internal
optimizations, such as scheduling and locality, to retrieve data from and store
data on heterogeneous hardware.
